Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-04-03 ConferencePaper/DraftEdwardsWoods.tex
Pre merge

% RECS data set is the 2009 publication.  12083 observations are included in the data, of which 11395 are included in the struture-tenure model. Combining dwelling type (dwltype) and the binary response variable Ownrent, Dwltype includes six categories as follows: single family detached house, townhouse (including duplex, or row house), small apartment complex, large apartment complex, mobile home. Mobile homes are notable for having considerably fewer observations than other categories. The model is based on the following variables: income, resident ages, education, and ethnicity.  Logged, midpoints, are used for income. Education is broken into six categories describing highest education level completed by the head of the household: elementary, some high school, high school. Some college/trade/vocational school, college graduate and post graduate degree.  The ethnicity variable is constructed from a composite of six dummy variables for head of households broken into head of households one and two.  The result is one variable for each where from one to six: Native American, Asian/Pacific Islander, Black/African American, Hispanic/Latino, White/Caucasian, and Other.  For our purposes head of household \#2 is ignored.

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:48 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:48 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
NE &  47 & 1173 & 218 & 326 & 470 \\ 
  MidWest &  92 & 2080 & 162 & 145 & 323 \\ 
  South & 245 & 2685 & 257 & 226 & 603 \\ 
  West & 137 & 1757 & 241 & 209 & 509 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-005}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:55 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & FALSE & TRUE \\ 
  \hline
FALSEWt & 7606 & 384 \\ 
  FALSEAfAm & 1367 &  88 \\ 
  FALSEAsian & 424 &  21 \\ 
  FALSEMulti & 133 &  13 \\ 
  FALSENativeAm &  68 &   5 \\ 
  FALSEOther & 102 &   9 \\ 
  FALSEPacific &  30 &   6 \\ 
  TRUEAfAm &  31 &   3 \\ 
  TRUEAsian &   4 &   2 \\ 
  TRUEMulti &  19 &   2 \\ 
  TRUENativeAm &  36 &   1 \\ 
  TRUEOther &  88 &  11 \\ 
  TRUEPacific &   4 &   0 \\ 
  TRUEWt & 1330 & 118 \\ 
   \hline
\end{tabular}
\caption{EnergyStar Wall AC by Race and Ethnicity} 
\label{tab:EnergyStarWall}
\end{table}

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:55 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Rural & Urban \\ 
  \hline
FALSEWt & 1937 & 6053 \\ 
  FALSEAfAm & 192 & 1263 \\ 
  FALSEAsian &  14 & 431 \\ 
  FALSEMulti &  28 & 118 \\ 
  FALSENativeAm &  25 &  48 \\ 
  FALSEOther &  12 &  99 \\ 
  FALSEPacific &   4 &  32 \\ 
  TRUEAfAm &   6 &  28 \\ 
  TRUEAsian &   0 &   6 \\ 
  TRUEMulti &   1 &  20 \\ 
  TRUENativeAm &   3 &  34 \\ 
  TRUEOther &   5 &  94 \\ 
  TRUEPacific &   2 &   2 \\ 
  TRUEWt & 137 & 1311 \\ 
   \hline
\end{tabular}
\caption{Race by Urban/Rural} 
\label{tab:UrbRural}
\end{table}

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:55 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & Other \\ 
  \hline
FALSEWt & 4077 & 315 & 361 &   3 & 3190 &  11 &  12 &   7 \\ 
  FALSEAfAm & 755 &  17 &  35 &   0 & 640 &   0 &   2 &   0 \\ 
  FALSEAsian & 312 &   7 &  12 &   0 & 109 &   0 &   0 &   2 \\ 
  FALSEMulti &  85 &   5 &   3 &   0 &  53 &   0 &   0 &   0 \\ 
  FALSENativeAm &  34 &   2 &   1 &   0 &  36 &   0 &   0 &   0 \\ 
  FALSEOther &  57 &   3 &   6 &   0 &  44 &   0 &   0 &   0 \\ 
  FALSEPacific &  15 &   0 &   2 &   0 &  17 &   0 &   2 &   0 \\ 
  TRUEAfAm &  20 &   0 &   1 &   0 &  13 &   0 &   0 &   0 \\ 
  TRUEAsian &   5 &   0 &   0 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEMulti &  12 &   0 &   1 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUENativeAm &  29 &   0 &   0 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUEOther &  62 &   1 &   5 &   0 &  30 &   0 &   0 &   0 \\ 
  TRUEPacific &   1 &   1 &   0 &   0 &   2 &   0 &   0 &   0 \\ 
  TRUEWt & 830 &  33 &  26 &   0 & 552 &   0 &   1 &   0 \\ 
   \hline
\end{tabular}
\caption{Water Service by Race and Ethnicity} 
\label{tab:Water}
\end{table}
% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:55 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & District & Other \\ 
  \hline
FALSEWt & 3987 & 400 & 642 &  40 & 2515 & 245 &   1 &  11 &  19 \\ 
  FALSEAfAm & 674 &  29 &  60 &   6 & 640 &  10 &   0 &   5 &   0 \\ 
  FALSEAsian & 249 &   1 &  21 &   0 & 122 &   1 &   0 &   2 &   0 \\ 
  FALSEMulti &  80 &   6 &   7 &   0 &  41 &   7 &   0 &   0 &   1 \\ 
  FALSENativeAm &  34 &   3 &   1 &   0 &  33 &   2 &   0 &   0 &   0 \\ 
  FALSEOther &  59 &   1 &   9 &   0 &  36 &   3 &   0 &   0 &   0 \\ 
  FALSEPacific &  16 &   0 &   2 &   0 &   5 &   1 &   0 &   0 &   0 \\ 
  TRUEAfAm &  21 &   0 &   1 &   1 &   9 &   0 &   0 &   0 &   0 \\ 
  TRUEAsian &   4 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 \\ 
  TRUEMulti &  11 &   0 &   4 &   0 &   4 &   1 &   0 &   0 &   0 \\ 
  TRUENativeAm &  26 &   1 &   2 &   0 &   7 &   0 &   0 &   0 &   0 \\ 
  TRUEOther &  53 &   0 &   8 &   1 &  32 &   0 &   0 &   2 &   0 \\ 
  TRUEPacific &   1 &   0 &   0 &   0 &   2 &   0 &   0 &   0 &   0 \\ 
  TRUEWt & 604 &  25 &  51 &   2 & 540 &  18 &   0 &   3 &   1 \\ 
   \hline
\end{tabular}
\caption{Heating Fuel by Race and Ethnicity} 
\label{tab:HeatFuel}
\end{table}
% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:55 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & VColdCold & HotDryMixedDry & HotHumid & MixedHumid & Marine \\ 
  \hline
FALSEWt & 3118 & 850 & 1216 & 2382 & 424 \\ 
  FALSEAfAm & 299 & 131 & 383 & 611 &  31 \\ 
  FALSEAsian &  95 & 128 &  60 &  77 &  85 \\ 
  FALSEMulti &  51 &  27 &  13 &  40 &  15 \\ 
  FALSENativeAm &  23 &  10 &   7 &  28 &   5 \\ 
  FALSEOther &  29 &  16 &  24 &  37 &   5 \\ 
  FALSEPacific &   4 &   6 &  13 &   4 &   9 \\ 
  TRUEAfAm &  16 &   5 &   4 &   9 &   0 \\ 
  TRUEAsian &   2 &   2 &   1 &   0 &   1 \\ 
  TRUEMulti &  12 &   6 &   1 &   0 &   2 \\ 
  TRUENativeAm &   9 &  14 &   1 &   8 &   5 \\ 
  TRUEOther &  35 &  19 &  10 &  28 &   7 \\ 
  TRUEPacific &   2 &   0 &   2 &   0 &   0 \\ 
  TRUEWt & 237 & 481 & 406 & 237 &  87 \\ 
   \hline
\end{tabular}
\caption{Climate by Race and Ethnicity} 
\label{tab:Climate}
\end{table}
\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
\includegraphics{DraftEdwardsWoods-013}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:57 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Never & ThreeDay & TwoDay & OneDay & FewWeek & OneWeek & LessWeek \\ 
  \hline
FALSEWt &  67 & 452 & 1814 & 3303 & 1825 & 254 & 275 \\ 
  FALSEAfAm &  11 & 156 & 351 & 341 & 448 &  80 &  68 \\ 
  FALSEAsian &   4 &  63 & 111 & 148 &  91 &  13 &  15 \\ 
  FALSEMulti &   2 &  14 &  45 &  40 &  36 &   7 &   2 \\ 
  FALSENativeAm &   0 &   7 &  22 &  27 &  11 &   3 &   3 \\ 
  FALSEOther &   2 &  10 &  25 &  21 &  43 &   3 &   7 \\ 
  FALSEPacific &   0 &   3 &   9 &  10 &  11 &   0 &   3 \\ 
  TRUEAfAm &   1 &   4 &   7 &  13 &   9 &   0 &   0 \\ 
  TRUEAsian &   0 &   0 &   1 &   3 &   2 &   0 &   0 \\ 
  TRUEMulti &   0 &   2 &   1 &  11 &   5 &   2 &   0 \\ 
  TRUENativeAm &   0 &   3 &  12 &  15 &   4 &   2 &   1 \\ 
  TRUEOther &   0 &  20 &  28 &  31 &  14 &   3 &   3 \\ 
  TRUEPacific &   0 &   3 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEWt &  22 & 208 & 453 & 435 & 226 &  42 &  62 \\ 
   \hline
\end{tabular}
\caption{Weekly Meals Cooked by Race and Ethnicity} 
\label{tab:Cooking}
\end{table}
\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
\includegraphics{DraftEdwardsWoods-015}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-4 package
% Thu Apr  2 14:49:57 2015
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & State & Population & Reports (per 100,000) \\ 
  \hline
1 & Alabama & 4,677,464 & 7.50 \\ 
  2 & Alaska & 688,125 & 13.01 \\ 
  3 & Arizona & 6,499,377 & 3.68 \\ 
  4 & Arkansas & 2,867,764 & 9.26 \\ 
  5 & California & 36,580,371 & 3.03 \\ 
  6 & Colorado & 4,935,213 & 1.97 \\ 
  7 & Connecticut & 3,502,932 & 20.50 \\ 
  8 & Delaware & 876,211 & 14.00 \\ 
  9 & District of Columbia & 590,074 & 14.00 \\ 
  10 & Florida & 18,423,878 & 3.93 \\ 
  11 & Georgia & 9,697,838 & 2.06 \\ 
  12 & Hawaii & 1,287,481 & 13.01 \\ 
  13 & Idaho & 1,527,506 & 9.94 \\ 
  14 & Illinois & 12,842,954 & 2.88 \\ 
  15 & Indiana & 6,388,309 & 9.14 \\ 
  16 & Iowa & 2,993,987 & 19.92 \\ 
  17 & Kansas & 2,797,375 & 10.31 \\ 
  18 & Kentucky & 4,287,931 & 7.50 \\ 
  19 & Louisiana & 4,451,513 & 9.26 \\ 
  20 & Maine & 1,319,691 & 20.50 \\ 
  21 & Maryland & 5,658,655 & 14.00 \\ 
  22 & Massachusetts & 6,543,595 & 4.51 \\ 
  23 & Michigan & 10,002,486 & 4.97 \\ 
  24 & Minnesota & 5,230,567 & 19.92 \\ 
  25 & Mississippi & 2,940,212 & 7.50 \\ 
  26 & Missouri & 5,956,335 & 4.99 \\ 
  27 & Montana & 968,035 & 9.94 \\ 
  28 & Nebraska & 1,781,949 & 10.31 \\ 
  29 & Nevada & 2,615,772 & 5.08 \\ 
  30 & New Hampshire & 1,321,872 & 20.50 \\ 
  31 & New Jersey & 8,663,398 & 2.34 \\ 
  32 & New Mexico & 1,986,763 & 5.08 \\ 
  33 & New York & 19,467,789 & 4.60 \\ 
  34 & North Carolina & 9,247,134 & 4.22 \\ 
  35 & North Dakota & 641,421 & 19.92 \\ 
  36 & Ohio & 11,528,072 & 9.14 \\ 
  37 & Oklahoma & 3,644,025 & 9.26 \\ 
  38 & Oregon & 3,782,991 & 13.01 \\ 
  39 & Pennsylvania & 12,566,368 & 1.87 \\ 
  40 & Rhode Island & 1,053,502 & 20.50 \\ 
  41 & South Carolina & 4,503,280 & 4.22 \\ 
  42 & South Dakota & 804,532 & 19.92 \\ 
  43 & Tennessee & 6,240,456 & 2.61 \\ 
  44 & Texas & 24,304,290 & 4.18 \\ 
  45 & Utah & 2,727,343 & 9.94 \\ 
  46 & Vermont & 621,049 & 20.50 \\ 
  47 & Virginia & 7,795,424 & 2.03 \\ 
  48 & Washington & 6,566,073 & 13.01 \\ 
  49 & West Virginia & 1,814,873 & 14.00 \\ 
  50 & Wisconsin & 5,627,610 & 1.81 \\ 
  51 & Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

@@

% The multinomial logit is first ran with owndwel as the dependent variable and the independent variables as follows: income, educ, race5, age_1, age_2.  The base chosen was that of house renters, represented here as the first category (see appendix).  Here, race5 represents whether the head of the household is white.  Running the multinomial logit with all raises included as independent variables proved problematic, and largely insignificant.  Ages of children were left separate in an attempt to model the difference between households with children of all ages and those with only young children.  Having only young children may represent households in starter homes who are not necessarily well established.  As well households with children over the age of eighteen are essentially ignored and treated as adults.  Another iteration of the model is also down removing the children variables and instead using resident count.
% The pseudo r-squared for the first model specified is 0.0912, which low it is important to bear in mind the problematic nature of interpreting pseudo r-squared values.

@@

This model is in general not very good at explaining square footage; the adjusted $R^2$ is only $.3897$.  This weakness will plague us later when we jointly estimate this model with structure type, tenure and electricity use, but illustrates one of the ways we can endogenize the choices that lead to electricity consumption.

>>>>

RECS data set is the 2009 publication.  12083 observations are included in the data, of which 11395 are included in the struture-tenure model. Combining dwelling type (dwltype) and the binary response variable Ownrent,Dwltype includes six categories as follows: single family detached house, townhouse (including duplex, or row house), small apartment complex, large apartment complex, mobile home. Mobile homes are notable for having considerably fewer observations than other categories. The model is based on the following variables: income, resident ages, education, and ethnicity.  Logged, midpoints, are used for income. Education is broken into six categories describing highest education level completed by the head of the household: elementary, some high school, high school. Some college/trade/vocational school, college graduate and post graduate degree.  The ethnicity variable is constructed from a composite of six dummy variables for head of households broken into head of households one and two.  The result is one variable for each where from one to six: Native American, Asian/Pacific Islander, Black/African American, Hispanic/Latino, White/Caucasian, and Other.  For our purposes head of household #2 is ignored.

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:34 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:34 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
NE &  47 & 1173 & 218 & 326 & 470 \\ 
  MidWest &  92 & 2080 & 162 & 145 & 323 \\ 
  South & 245 & 2685 & 257 & 226 & 603 \\ 
  West & 137 & 1757 & 241 & 209 & 509 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-005}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:50 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & FALSE & TRUE \\ 
  \hline
FALSEWt & 7606 & 384 \\ 
  FALSEAfAm & 1367 &  88 \\ 
  FALSEAsian & 424 &  21 \\ 
  FALSEMulti & 133 &  13 \\ 
  FALSENativeAm &  68 &   5 \\ 
  FALSEOther & 102 &   9 \\ 
  FALSEPacific &  30 &   6 \\ 
  TRUEAfAm &  31 &   3 \\ 
  TRUEAsian &   4 &   2 \\ 
  TRUEMulti &  19 &   2 \\ 
  TRUENativeAm &  36 &   1 \\ 
  TRUEOther &  88 &  11 \\ 
  TRUEPacific &   4 &   0 \\ 
  TRUEWt & 1330 & 118 \\ 
   \hline
\end{tabular}
\caption{EnergyStar Wall AC by Race and Ethnicity} 
\label{tab:EnergyStarWall}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:50 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Rural & Urban \\ 
  \hline
FALSEWt & 1937 & 6053 \\ 
  FALSEAfAm & 192 & 1263 \\ 
  FALSEAsian &  14 & 431 \\ 
  FALSEMulti &  28 & 118 \\ 
  FALSENativeAm &  25 &  48 \\ 
  FALSEOther &  12 &  99 \\ 
  FALSEPacific &   4 &  32 \\ 
  TRUEAfAm &   6 &  28 \\ 
  TRUEAsian &   0 &   6 \\ 
  TRUEMulti &   1 &  20 \\ 
  TRUENativeAm &   3 &  34 \\ 
  TRUEOther &   5 &  94 \\ 
  TRUEPacific &   2 &   2 \\ 
  TRUEWt & 137 & 1311 \\ 
   \hline
\end{tabular}
\caption{Race by Urban/Rural} 
\label{tab:UrbRural}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:50 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & Other \\ 
  \hline
FALSEWt & 4077 & 315 & 361 &   3 & 3190 &  11 &  12 &   7 \\ 
  FALSEAfAm & 755 &  17 &  35 &   0 & 640 &   0 &   2 &   0 \\ 
  FALSEAsian & 312 &   7 &  12 &   0 & 109 &   0 &   0 &   2 \\ 
  FALSEMulti &  85 &   5 &   3 &   0 &  53 &   0 &   0 &   0 \\ 
  FALSENativeAm &  34 &   2 &   1 &   0 &  36 &   0 &   0 &   0 \\ 
  FALSEOther &  57 &   3 &   6 &   0 &  44 &   0 &   0 &   0 \\ 
  FALSEPacific &  15 &   0 &   2 &   0 &  17 &   0 &   2 &   0 \\ 
  TRUEAfAm &  20 &   0 &   1 &   0 &  13 &   0 &   0 &   0 \\ 
  TRUEAsian &   5 &   0 &   0 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEMulti &  12 &   0 &   1 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUENativeAm &  29 &   0 &   0 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUEOther &  62 &   1 &   5 &   0 &  30 &   0 &   0 &   0 \\ 
  TRUEPacific &   1 &   1 &   0 &   0 &   2 &   0 &   0 &   0 \\ 
  TRUEWt & 830 &  33 &  26 &   0 & 552 &   0 &   1 &   0 \\ 
   \hline
\end{tabular}
\caption{Water Service by Race and Ethnicity} 
\label{tab:Water}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:50 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & District & Other \\ 
  \hline
FALSEWt & 3987 & 400 & 642 &  40 & 2515 & 245 &   1 &  11 &  19 \\ 
  FALSEAfAm & 674 &  29 &  60 &   6 & 640 &  10 &   0 &   5 &   0 \\ 
  FALSEAsian & 249 &   1 &  21 &   0 & 122 &   1 &   0 &   2 &   0 \\ 
  FALSEMulti &  80 &   6 &   7 &   0 &  41 &   7 &   0 &   0 &   1 \\ 
  FALSENativeAm &  34 &   3 &   1 &   0 &  33 &   2 &   0 &   0 &   0 \\ 
  FALSEOther &  59 &   1 &   9 &   0 &  36 &   3 &   0 &   0 &   0 \\ 
  FALSEPacific &  16 &   0 &   2 &   0 &   5 &   1 &   0 &   0 &   0 \\ 
  TRUEAfAm &  21 &   0 &   1 &   1 &   9 &   0 &   0 &   0 &   0 \\ 
  TRUEAsian &   4 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 \\ 
  TRUEMulti &  11 &   0 &   4 &   0 &   4 &   1 &   0 &   0 &   0 \\ 
  TRUENativeAm &  26 &   1 &   2 &   0 &   7 &   0 &   0 &   0 &   0 \\ 
  TRUEOther &  53 &   0 &   8 &   1 &  32 &   0 &   0 &   2 &   0 \\ 
  TRUEPacific &   1 &   0 &   0 &   0 &   2 &   0 &   0 &   0 &   0 \\ 
  TRUEWt & 604 &  25 &  51 &   2 & 540 &  18 &   0 &   3 &   1 \\ 
   \hline
\end{tabular}
\caption{Heating Fuel by Race and Ethnicity} 
\label{tab:HeatFuel}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:50 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & VColdCold & HotDryMixedDry & HotHumid & MixedHumid & Marine \\ 
  \hline
FALSEWt & 3118 & 850 & 1216 & 2382 & 424 \\ 
  FALSEAfAm & 299 & 131 & 383 & 611 &  31 \\ 
  FALSEAsian &  95 & 128 &  60 &  77 &  85 \\ 
  FALSEMulti &  51 &  27 &  13 &  40 &  15 \\ 
  FALSENativeAm &  23 &  10 &   7 &  28 &   5 \\ 
  FALSEOther &  29 &  16 &  24 &  37 &   5 \\ 
  FALSEPacific &   4 &   6 &  13 &   4 &   9 \\ 
  TRUEAfAm &  16 &   5 &   4 &   9 &   0 \\ 
  TRUEAsian &   2 &   2 &   1 &   0 &   1 \\ 
  TRUEMulti &  12 &   6 &   1 &   0 &   2 \\ 
  TRUENativeAm &   9 &  14 &   1 &   8 &   5 \\ 
  TRUEOther &  35 &  19 &  10 &  28 &   7 \\ 
  TRUEPacific &   2 &   0 &   2 &   0 &   0 \\ 
  TRUEWt & 237 & 481 & 406 & 237 &  87 \\ 
   \hline
\end{tabular}
\caption{Climate by Race and Ethnicity} 
\label{tab:Climate}
\end{table}
\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
\includegraphics{DraftEdwardsWoods-013}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Never & ThreeDay & TwoDay & OneDay & FewWeek & OneWeek & LessWeek \\ 
  \hline
FALSEWt &  67 & 452 & 1814 & 3303 & 1825 & 254 & 275 \\ 
  FALSEAfAm &  11 & 156 & 351 & 341 & 448 &  80 &  68 \\ 
  FALSEAsian &   4 &  63 & 111 & 148 &  91 &  13 &  15 \\ 
  FALSEMulti &   2 &  14 &  45 &  40 &  36 &   7 &   2 \\ 
  FALSENativeAm &   0 &   7 &  22 &  27 &  11 &   3 &   3 \\ 
  FALSEOther &   2 &  10 &  25 &  21 &  43 &   3 &   7 \\ 
  FALSEPacific &   0 &   3 &   9 &  10 &  11 &   0 &   3 \\ 
  TRUEAfAm &   1 &   4 &   7 &  13 &   9 &   0 &   0 \\ 
  TRUEAsian &   0 &   0 &   1 &   3 &   2 &   0 &   0 \\ 
  TRUEMulti &   0 &   2 &   1 &  11 &   5 &   2 &   0 \\ 
  TRUENativeAm &   0 &   3 &  12 &  15 &   4 &   2 &   1 \\ 
  TRUEOther &   0 &  20 &  28 &  31 &  14 &   3 &   3 \\ 
  TRUEPacific &   0 &   3 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEWt &  22 & 208 & 453 & 435 & 226 &  42 &  62 \\ 
   \hline
\end{tabular}
\caption{Weekly Meals Cooked by Race and Ethnicity} 
\label{tab:Cooking}
\end{table}
\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
\includegraphics{DraftEdwardsWoods-015}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Thu Apr  2 18:57:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & State & Population & Reports (per 100,000) \\ 
  \hline
1 & Alabama & 4,677,464 & 7.50 \\ 
  2 & Alaska & 688,125 & 13.01 \\ 
  3 & Arizona & 6,499,377 & 3.68 \\ 
  4 & Arkansas & 2,867,764 & 9.26 \\ 
  5 & California & 36,580,371 & 3.03 \\ 
  6 & Colorado & 4,935,213 & 1.97 \\ 
  7 & Connecticut & 3,502,932 & 20.50 \\ 
  8 & Delaware & 876,211 & 14.00 \\ 
  9 & District of Columbia & 590,074 & 14.00 \\ 
  10 & Florida & 18,423,878 & 3.93 \\ 
  11 & Georgia & 9,697,838 & 2.06 \\ 
  12 & Hawaii & 1,287,481 & 13.01 \\ 
  13 & Idaho & 1,527,506 & 9.94 \\ 
  14 & Illinois & 12,842,954 & 2.88 \\ 
  15 & Indiana & 6,388,309 & 9.14 \\ 
  16 & Iowa & 2,993,987 & 19.92 \\ 
  17 & Kansas & 2,797,375 & 10.31 \\ 
  18 & Kentucky & 4,287,931 & 7.50 \\ 
  19 & Louisiana & 4,451,513 & 9.26 \\ 
  20 & Maine & 1,319,691 & 20.50 \\ 
  21 & Maryland & 5,658,655 & 14.00 \\ 
  22 & Massachusetts & 6,543,595 & 4.51 \\ 
  23 & Michigan & 10,002,486 & 4.97 \\ 
  24 & Minnesota & 5,230,567 & 19.92 \\ 
  25 & Mississippi & 2,940,212 & 7.50 \\ 
  26 & Missouri & 5,956,335 & 4.99 \\ 
  27 & Montana & 968,035 & 9.94 \\ 
  28 & Nebraska & 1,781,949 & 10.31 \\ 
  29 & Nevada & 2,615,772 & 5.08 \\ 
  30 & New Hampshire & 1,321,872 & 20.50 \\ 
  31 & New Jersey & 8,663,398 & 2.34 \\ 
  32 & New Mexico & 1,986,763 & 5.08 \\ 
  33 & New York & 19,467,789 & 4.60 \\ 
  34 & North Carolina & 9,247,134 & 4.22 \\ 
  35 & North Dakota & 641,421 & 19.92 \\ 
  36 & Ohio & 11,528,072 & 9.14 \\ 
  37 & Oklahoma & 3,644,025 & 9.26 \\ 
  38 & Oregon & 3,782,991 & 13.01 \\ 
  39 & Pennsylvania & 12,566,368 & 1.87 \\ 
  40 & Rhode Island & 1,053,502 & 20.50 \\ 
  41 & South Carolina & 4,503,280 & 4.22 \\ 
  42 & South Dakota & 804,532 & 19.92 \\ 
  43 & Tennessee & 6,240,456 & 2.61 \\ 
  44 & Texas & 24,304,290 & 4.18 \\ 
  45 & Utah & 2,727,343 & 9.94 \\ 
  46 & Vermont & 621,049 & 20.50 \\ 
  47 & Virginia & 7,795,424 & 2.03 \\ 
  48 & Washington & 6,566,073 & 13.01 \\ 
  49 & West Virginia & 1,814,873 & 14.00 \\ 
  50 & Wisconsin & 5,627,610 & 1.81 \\ 
  51 & Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

@@

The multinomial logit is first ran with owndwel as the dependent variable and the independent variables as follows: income, educ, race5, age_1, age_2.  The base chosen was that of house renters, represented here as the first category (see appendix).  Here, race5 represents whether the head of the household is white.  Running the multinomial logit with all raises included as independent variables proved problematic, and largely insignificant.  Ages of children were left separate in an attempt to model the difference between households with children of all ages and those with only young children.  Having only young children may represent households in starter homes who are not necessarily well established.  As well households with children over the age of eighteen are essentially ignored and treated as adults.  Another iteration of the model is also down removing the children variables and instead using resident count.
The pseudo r-squared for the first model specified is 0.0912, which low it is important to bear in mind the problematic nature of interpreting pseudo r-squared values.

@@
